{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-07 Paper/main.tex
Making Bspline truncation more precise.

	This, however, does not really lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$. To focus on specific approximation errors in the later parts of this paper, we will, however, assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen number of B-spline basis functions. 
	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.

@@

	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$. The number $L$ can be chosen subjectively, but also through applying a data-driven method such as Cross-Validation. Figure \ref{Different_Expansions} shows the effect of choosing different truncation parameters for the case of the Near-Infrared Spectroscopy dataset which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the parameter choice.

>>>>

	This, however, does not really lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$. To focus on specific approximation errors in the later parts of this paper, we will, however, assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen number of B-spline basis functions. 
	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool. \\

	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases have, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper. For the sake of keeping the notation reasonably concise, we will still keep this notation. However, by convention, this shall mean using a B-spline basis consisting of $L$ functions from this point on.

@@

	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$. The number $L$ can be chosen subjectively, but also through applying a data-driven method such as Cross-Validation. Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation for the case of the Near-Infrared Spectroscopy dataset which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the parameter choice.
